---
title: "Writing up the results"
author: ""
date: " "
institute: " "
output:
  xaringan::moon_reader:
    css: ["ninjutsu", "style.css"]  # include your custom style
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```


### Results for H1

We conducted a proportion test to examine whether transfers from **State to Nonstate** institutions occur more frequently than transfers from **Nonstate to State** institutions.
We tested our hypothesis that *"transfers from state to non-state sectors are more likely than career transfers from non-state to state"*. Mathetimatically, this defines our null and alternate hypothesis as follows. 

$$H_{null}  : \text{State_to_Nonstate} \leq  \text{Nonstate_to_State}$$
$$H_{alt}  : \text{State_to_Nonstate} >  \text{Nonstate_to_State}$$
This test is done uisng a proportion test with the R function `prop.test`. 


##### Now explain brief what the proportion test is about and why it is suitable in this case


--- 

```{r, eval=FALSE}
category_map3 <- list(

  "Intra_NS_to_S"      =   c("EDU_IG_EDU_INST", "EDU_IG_EDU_GOV"),
  
  "Intra_S_to_NS"      =  c("EDU_INST_EDU_IG", "EDU_GOV_EDU_IG"),
  
  "Inter_NS_to_S"      =  c("EDU_IG_OTH_GOV", "EDU_IG_PARL", 
                            "EDU_IG_LOC_GOV"),
  
  "Inter_S_to_NS"   =     c("OTH_GOV_EDU_IG", "PARL_EDU_IG", 
                            "LOC_GOV_EDU_IG")
)

dd_filtered3 <- ddf_long_clean %>%
  filter(transfer_value %in% unlist(category_map)) %>%
  mutate(transfer_pattern = case_when(
    transfer_value %in% c(category_map$Intra_NS_to_S,category_map$Inter_NS_to_S) ~ "Nonstate_State",
    transfer_value %in% c(category_map$Intra_S_to_NS,category_map$Inter_S_to_NS) ~ "State_Nonstate"
  ))


unique(dd_filtered3$transfer_pattern)

state_to_nonstate <- sum(na.omit(dd_filtered3$transfer_pattern) == "State_Nonstate")
nonstate_to_state <- sum(na.omit(dd_filtered3$transfer_pattern) == "Nonstate_State")



x <- c(state_to_nonstate, nonstate_to_state)  
n <- c(state_to_nonstate + nonstate_to_state, 
       state_to_nonstate + nonstate_to_state)  # total in both groups (same)

prop.test(x = x, n=n, alternative = "greater")

```

---

#### Interpretation of our results

```2-sample test for equality of proportions with continuity correction data:  x out of n
X-squared = 776.6, df = 1, p-value < 2.2e-16
alternative hypothesis: greater
95 percent confidence interval:
 0.5236642 1.0000000
sample estimates:
   prop 1    prop 2 
0.7757812 0.2242187``` 




The p-value is extremely small (less than 2.2e-16), indicating that the difference between the two proportions is statistically significant. Therefore, we reject the null hypothesis of equal proportions.

We conclude that transfers from State to Nonstate institutions occur significantly more frequently than transfers in the opposite direction.

The 95% confidence interval for the difference in proportions ranges from approximately 52% to 100%, indicating a substantial and statistically reliable difference.

